Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-26 manuscript.Rmd
Address reviewer comments

## Data Preparation
### Social Cohesion Metric
The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus. Retweets were included in the corpus and used in the social cohesion calculation, as they indicate strong support for an individual’s message. Stop words, punctuations, and duplicate words were not removed from the tweets.

@@

```{r plot-mode-event, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Mode ICEWS event per day.'}

>>>>

## Data Preparation
### Social Cohesion Metric
The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus. Retweets were included in the corpus and used in the social cohesion calculation, as they indicate strong support for an individual’s message. Stop words, punctuations, and duplicate words were not removed from the tweets. The lengths of tweets were disregarded, as the aspect of interest is in shared linguistic content and not breadth of description.

@@

```{r plot-mode-event, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'A  plot of the most frequently documented ICEWS event score per day.'}
